To log or not to log

### 2022-06-08 main.tex
update manuscript

\subsection{Relative importance when summarising scores}
For a single transformation, the ranking between models is preserved, even though the numeric value of the score changes. However, when averaging across forecasts, the relative influence of individual forecasts on the aggregate score may differ dramatically, leading to changes in the overall model rankings. While the main rationale for applying the log transformation is that this better reflects the types of errors common in epidemiological modelling, it may also be helpful when scores based on the natural scale are very unequal. This usually happens, for example, when different forecast targets, like reported case numbers, hospitalisations and deaths, or the same targets across time and space, have very different orders of magnitude. In these instances, scores (even for an ideal forecaster) usually also differ by several orders of magnitude. When scores are aggregated on the natural scale without any prior transformation, overall performance would be dominated by the performance on the target which has the highest absolute numbers. After the log transformation, equal weight would be put on the relative performance, making performance across different targets more easily comparable (as scores of an ideal forecaster would not differ as much as on the natural scale).

While on the natural scale, aggregate forecasts will usually be dominated by predictions of quantities with high absolute values, the opposite may be true for scores based on log transformed predictions. Small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. The strength of this effect depends on the exact relationship between the mean and the variance of the quantity of interest.

ADD TO FIGURE CAPTION? 
To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

One way to handle situations where scores are very unequal, as mentioned above, is to add a number $n$ to all forecasts and observations in order to reduce the relative weight of forecast targets with small quantities.

Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \citep{Bracher} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high. 
% Maybe make a plot with one country and scores for that one country in different waves. We could then argue that within one wave, performance of the peak is meaningful, but across different waves (with different numbers) it is unclear, whether that difference conveys meaningful information.

>>>>

\subsection{Relative importance when summarising scores}
For a single transformation, the ranking between models is preserved, even though the numeric value of the score changes. However, when averaging across forecasts, the relative influence of individual forecasts on the aggregate score may differ dramatically, leading to changes in the overall model rankings. While the main rationale for applying the log transformation is that this better reflects the types of errors common in epidemiological modelling, it may also be helpful when scores based on the natural scale are very unequal. This usually happens, for example, when different forecast targets, like reported case numbers, hospitalisations and deaths, or the same targets across time and space, have very different orders of magnitude. In these instances, scores (even for an ideal forecaster) usually also differ by several orders of magnitude. Evaluating forecasts based on relative errors often makes it easier to compare performance across different targets more easily (as scores of an ideal forecaster would not differ as much as on the natural scale).

While on the natural scale, aggregate scores will usually be dominated by predictions of quantities with high absolute values, the opposite may be true for scores based on log transformed predictions. Small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. The strength of this effect depends on the exact relationship between the mean and the variance of the quantity of interest. For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. As mentioned above, one way to handle situations where scores are very unequal, is to add a number $n$ to all forecasts and observations in order to reduce the relative weight of forecast targets with small quantities.

% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

COULD ALSO BE DISCUSSION
Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \citep{Bracher} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high. 
% Maybe make a plot with one country and scores for that one country in different waves. We could then argue that within one wave, performance of the peak is meaningful, but across different waves (with different numbers) it is unclear, whether that difference conveys meaningful information.
